Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Remove term-only equation from the definition of [| |]

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq && \top																						  \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq && [| \nonterm G |] \land [| \{x/v\} \nonterm r |]  \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq && [| \nonterm r_1 |] \land [| \nonterm r_2 |]      \\
  & [| \nonterm{es} |]                                      && \triangleq && \text{oracle}(\nonterm{es})                      \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq && \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)   \\
\end{aligned}
\end{equation}

The last two equations represent the assumption
that the oracle knows how to translate the elementary refinements being the terms $\nonterm{es}$
or equality propositions $\nonterm{es}_1 = \nonterm{es}_2$.

>>>>

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq && \top																						  \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq && [| \nonterm G |] \land [| \{x/v\} \nonterm r |]  \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq && [| \nonterm r_1 |] \land [| \nonterm r_2 |]      \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq && \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)   \\
\end{aligned}
\end{equation}

The last equation represents the assumption
that the oracle knows how to translate the atomic refinements.
